Constructing a universe for the setoid model

### 2021-01-16 paper.tex
further work

>>>>

It is known that finitary IITs can be reduced to inductive types in an
extensional setting \cite{induction-is-enough}. In our paper we reduce
an infinitary IIT to inductive types in an intensional setting. In the
future, we would like to investigate whether this reduction can be
generalised to arbitrary infinitary IITs.
